% LaTeX resume using res.cls
\documentclass[line,margin]{res} 

\def\myauthor{Tian Cao}
\def\mytitle{tc-vita}
\def\myemail{tiancao@cs.unc.com}
\def\myweb{tiancao.me}
\def\myphone{(919) 699-9542}
\def\mykeywords{
	tian cao, 
	resume, 
	curriculum, 
	vita, 
	curriculum vita, 
	cv, 
	tian, 
	cao, 
	tc
}


\usepackage[svgnames]{xcolor}
\usepackage[strict]{changepage}
\usepackage{fontawesome}
\usepackage[
ocgcolorlinks,
urlcolor=DarkSlateBlue, %urlcolor={[rgb]{0,0,0.54}},
citecolor=DarkSlateBlue, 
filecolor=DarkSlateBlue,
unicode,
plainpages=false,
pdfpagelabels,
pdftitle={\mytitle},
pdfauthor={\myauthor},
pdfkeywords={\mykeywords}
]{hyperref}
\usepackage{hyperref}


%\usepackage{fontawesome}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\setlength{\oddsidemargin}{-.4in}
\setlength{\evensidemargin}{-.4in}
\setlength{\textwidth}{6.0in}
%\setlength{\itemsep}{0in}
%\setlength{\parsep}{0in}

\setlength{\topmargin}{-.6in} %{-0.05in}  % Start text higher on the page
\setlength{\footskip}{.2in}
\setlength{\textheight}{10.0in}  % increase textheight to fit more on a page
%\setlength{\headsep}{0.2in}     % space between header and text
%\setlength{\headheight}{12pt}   % make room for header

\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
%\rfoot{Tian Cao  (\thepage/ 2)\\ \hspace*{-\sectionwidth}\emph{tiancao@cs.unc.edu} }  % put page number at right

\newenvironment{bullets}{\begin{list}{\tiny$\bullet$}{\topsep 0pt \itemsep -2pt \leftmargin .15in}}{\vspace*{4pt}\end{list}}

\rfoot{Tian Cao  (\thepage/2) }  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
      
{\def\section*#1{}\bibliography{ref}}
%\nocite{*}

\begin{document}

\begin{adjustwidth}{-1.3in}{}
	{\Huge
		{\textsc{%
				{\addfontfeature{Style=TitlingCaps}T}\kern-1.5ptian
				{\addfontfeature{Style=TitlingCaps}C}ao}
		}
	}
	\hfill\hfill\hfill
	{
		\begin{minipage}[b]{2in}
			\flushleft %\footnotesize 
			100 Rock Haven Road \\ 
			APT E208 \\ 
			Carrboro, NC~~27510
		\end{minipage}
		\hfill
		\begin{minipage}[b]{1.8in}
			\flushright %\footnotesize 
			(919) 699-9542 \, \faPhone \\ 
			\texttt{\href{mailto:tiancao@cs.unc.edu}{tiancao@cs.unc.edu}}\, \faEnvelope \\
			\texttt{\href{http://tiancao.me/}{tiancao.me}}\, \faGlobe 
		\end{minipage}
	}\par
	%\hrulefill
\end{adjustwidth}  

%\name{\huge{\sc Tian Cao} \vspace*{.1in}}
% \address used twice to have two lines of address
%\address{1985  Storm Lane, Troy, NY 12180}
%\address{(518) 273-0014 or (518) 272-6666}

\begin{resume}
%\section{\sc{Contact Information}}
%\smallskip
%%\begin{tabular}{@{}p{3in}p{3in}}
%%\begin{tabular}{@{} l r}
%%\begin{tabular}{@{}p{3in} r}
%Department of Computer Science  \hfill { Mobile:}  (+1) 919-699-9542 \\
%%Campus Box 3175, Sitterson Hall  \hfill { Office phone:} (+1) 919-843-7425 \\      
%UNC-Chapel Hill \hfill { Email:}  tiancao@cs.unc.edu \\
%Chapel Hill, NC 27599-3175 USA \hfill  \url{http://tiancao.me/} 
%%\end{tabular}

%\section{\sc{Objective}}       
%%\smallskip
%
%Full-time R\&D position
%
%\vspace{-.05in}
\section{\sc{Interests}}       
%\smallskip

Machine Learning, Image Analysis, Computer Vision %\\
%Deep Learning, Dictionary Learning, Image Classification



\section{\sc Education}
\smallskip

\textsc{\textbf{University of North Carolina at Chapel Hill}}, Chapel Hill, NC \hfill{08/2015(expected)}\\
\vspace*{-.15in}
\begin{list1}
\item[] Ph.D. candidate in Computer Science %\hfill{GPA: 3.7/4.0}
%\item[] Dissertation title: Coupled Dictionary Learning for Image Analysis
\end{list1}
% \smallskip
\vspace*{-.15in}
\textsc{\textbf{Sichuan University}}, Chengdu, Sichuan, China \hfill {06/2010} \\
\vspace*{-.15in}
\begin{list1}
\item[] M.S. in Computer Science  %\hfill {GPA: 3.7/4.0}
\end{list1}
 %\smallskip
\vspace*{-.15in}
\textsc{\textbf{Sichuan University}}, Chengdu, Sichuan, China \hfill{05/2007}\\
\vspace*{-.15in}
\begin{list1}
\item[] B.E. in Computer Science  %\hfill {GPA: 3.6/4.0}
\end{list1}

\section{\sc Skills}
\smallskip

C/C++, Java, Matlab, Python, Bash, CUDA, OPENCV


\vspace{-.05in}
\section{\sc Experience}
\smallskip

\textbf{Research Assistant, UNC Chapel Hill}, Chapel Hill, NC  \hfill      09/2010-present \\
Coupled Dictionary Learning for Image Analysis %\hfill {Advisor: Marc Niethammer}
\begin{bullets}
	\item Developed coupled dictionary learning methods for image analysis.
	\item Learning coupled dictionaries based on sparse coding, and applied the learned dictionary to simplify the multi-modal image analysis problems.
	%\item Applied the algorithm to Correlative Microscope images.
	\item Implemented in matlab and C++.
\end{bullets}
\vspace{-.1in}


\textbf{Research Intern, IBM Almaden Research Center}, San Jose, CA \hfill      05/2014-08/2014 \\
%  \hfill {Supervisor: Peng Wang}\\
Multi-atlas based Image Segmentation
\begin{bullets} 
\item Investigated methods of learning from ambiguous labels.
\item Investigated atlas based image segmentation methods with different local features and classifiers.
\item Implemented atlas based image segmentation framework in Java and matlab.
\end{bullets}
%\vspace{.05in} %\smallskip 
%\section{\sc Research Experience} 
%\smallskip
\vspace{-.1in}

\textbf{Research Intern, Siemens Corporate Research}, Princeton, NJ \hfill      05/2012-08/2012 \\
%  \hfill {Supervisor: Peng Wang}\\
Real-time Object Detection in Ultrasound Videos
\begin{bullets} 
\item Developed and implemented a needle detection method for ultrasound videos. 
\item Incorporated with different features and hough transform to vote the needle segment.
\item Implemented a 3D steerable filtering method to incorporate spatial and temporal information for needle detection in C++.

\end{bullets}
%\vspace{.05in} %\smallskip 
%\section{\sc Research Experience} 
%\smallskip
\vspace{-.1in}

 %\smallskip 
%\textbf{Deformable Registration with built-in Invariant to Affine Transformations} \hfill      2010-2011 \\
%\textit{ Research Assistant} at UNC Chapel Hill \hfill {Advisor: Marc Niethammer}\\
%Developed a deformable registration algorithm with built-in affine transformations, which can update the affine transformation at each deformable registration iteration, and
%applied this algorithm to the registration between fluorescence microscopy and TEM images.
%\smallskip \\
\textbf{Research Assistant, Chinese Academy of Sciences}, Shenzhen, China   \hfill      09/2009-03/2010 \\ %\hfill {Advisor: Yangsheng Xu}\\
Energy based Crowd Motion Analysis
\begin{bullets}
\item Developed an energy based crowd motion analysis algorithm based on mutual information.
\item Applied the algorithm to detect the crowd abnormal behaviors.
\item Implemented in OPENCV and C++.
\end{bullets}
\vspace{-.1in}

%\smallskip 
\textbf{Research Assistant, Sichuan University}, Chengdu, China \hfill      01/2008-09/2009 \\%\hfill {Advisor: Dong C. Liu}\\
Super-resolution for Ultrasound Speckle Reduction
\begin{bullets}
\item Developed a fast and robust super-resolution method for intima reconstruction in
ultrasound. 
\item Applied anisotropic diffusion to reduce speckle with edge enhancement in image reconstruction.
\item Implemented anisotropic diffusion method in C++ and GLSL.
\end{bullets} %\vspace{.05in} %\smallskip 
%\textbf{Motion Estimation and Visualization for Cardiac Ultrasound} \hfill      2008-2009 \\
%\textit{Research Assistant} at SCU \hfill {Advisor: Dong C. Liu}\\
%Developed a novel method for motion estimation and visualization of cardiac ultrasound images. The motion vector fields are derived from an adaptive curve region based matching algorithm.

\vspace{-.1in}


\section{\sc Publications}  
\smallskip
$[1]$.\textbf{Tian Cao}, Nikhil Singh, Vladimir Jojic, Marc Niethammer, ``Semi-coupled Dictionary Learning for Deformation Prediction'', \emph{International Symposium on Biomedical Imaging} (\textbf{ISBI}), 2015. \vspace{.05in}\\
$[2]$.\textbf{Tian Cao}, Christopher Zach, Marc Niethammer et al., ``Multi-modal Registration for Correlative Microscopy using Image Analogies'', \emph{Medical Image Analysis} (\textbf{MedIA}), Elsevier, 2014. \vspace{.05in}\\
$[3]$.\textbf{Tian Cao}, Vladimir Jojic, Marc Niethammer et al., ``Robust Multimodal Dictionary Learning'', \emph{The 16th International Conference on Medical Image Computing and Computer Assisted Intervention} (\textbf{MICCAI}), 2013. \vspace{.05in}\\ 
$[4]$.\textbf{Tian Cao}, Christopher Zach, Marc Niethammer et al., ``Registration for Correlative Microscopy using Image Analogies'',  \emph{Fifth Workshop on Biomedical Image Registration} (\textbf{WBIR}), 2012. \vspace{.05in}\\%\smallskip \textbf{Oral Presentation}.
$[5]$.Bo Wang, \textbf{Tian Cao}, Yuguo Dai, Dong C. Liu, ``Ultrasound Speckle Reduction via Super Resolution and Nonlinear Diffusion'',  \emph{the 9th Asian Conference on Computer Vision} (\textbf{ACCV}), 2009. \vspace{.05in}\\
%\smallskip
$[6]$.\textbf{Tian Cao}, Bo Wang, Dong C. Liu, ``Optimized GPU Framework of Semi-implicit AOS
Scheme Based Speckle Reducing Nonlinear Diffusion'',  \emph{proceedings of SPIE Medical Imaging} (\textbf{SPIE MI}), 2009.\vspace{.05in}\\%\smallskip  
$[7]$.\textbf{Tian Cao}, Chaowei Tan, Dong C. Liu, ``Adaptive Curve Region based Motion Estimation and Motion Visualization of Cardiac Ultrasound Imaging'',  \emph{the 3rd International Conference on Bioinformatics and Biomedical Engineering} (\textbf{ICBBE}), 2009.\vspace{.05in}\\
%\smallskip
$[8]$.\textbf{Tian Cao}, Xinyu Wu, Jinnian Guo, Shiqi Yu, Yangsheng Xu, ``Abnormal Crowd Motion Analysis'', \emph{IEEE International Conference on Robotics and Biomimetics} (\textbf{ROBIO}), 2009.

%\section{\sc Conference Talk} 
%\smallskip
%
%\textbf{Workshop on Biomedical Image Registration} \hfill      07/2012 \\
%Vanderbilt University, Nashville, TN, USA  \hfill \\%{Supervisor: Peng Wang}\\
%Topic:  Registration for Correlative Microscopy using Image Analogies \vspace{.05in}


 
\section{\sc Honors \& Awards}
%\smallskip

%{\renewcommand\baselinestretch{1.1}\selectfont
ISBI 2015 NIH Traval Award. \hfill      2015\\
Guanghua Scholarship.  \hfill       2010\\
Outstanding graduate Student Award, Sichuan University. \hfill       2010\\
Graduate Student Fellowship, Sichuan University.  \hfill       2007-2010\\
%Excellent graduate for Undergraduate Students, Sichuan University.  \hfill       2007\\
Student Innovation Award, Sichuan University.  \hfill        2005-2007 \\%\vspace{.1in}\\
1st prize of China Undergraduate Mathematical Contest in Modeling.  \hfill       2006



%\par}
\end{resume}

%\bibliography{ref}
%\bibliographystyle{plain}
\end{document}







